\documentclass[margin]{res}

\setlength{\textwidth}{5.1in} % set width of text portion
\usepackage{hyperref}
\hypersetup{
    colorlinks=false,
    linkcolor=black,      
    urlcolor=black,
}
\urlstyle{same}


\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Alexander Spangher}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{(631) 487-7777 or alexander.spangher@nytimes.com; New York City, NY}


\begin{resume}

\section{EDUCATION} {\bf Columbia University}, M.S. in Journalism \hfill {\sl Class of 2018}\\
{\bf Columbia University}, M.S. in Data Science \hfill {\sl Class of 2017}\\
				   {\bf Columbia University}, B.S. in Neuroscience {\sl and} B.S. in C.S. \hfill {\sl Class of 2014}
					% \sl will be bold italic in New Century Schoolbook (or any postscript font) and just slanted in Computer Modern (default) font


\section{RELEVANT \\ EXPERIENCE} 
{\sl \bf New York Times}, NYC, NY {\sl Data Scientist} \hfill {\it 2014- present}\\
\begin{itemize}
\item Designed and implemented LDA-based article recommendation algorithm, scaled to all users. Built using Luigi-powered data pipelines, MySQL data storage, and WSGI API layer. See blogpost: \url{https://open.blogs.nytimes.com/2015/08/11/building- the-next-new-york-times-recommendation-engine/.}
\item Launched ML tools to improve newsroom processes. Used unsupervised variational and embedding approaches and NLP feature engineering. Designed architecture using Google Cloud Services: DataStore, GKE and BigQuery.
\item Used MTurk to crowd-source emotion-tags for articles. Constructed classifiers to learn these tags with deep and shallow approaches. Developed distributed gridsearch pipeline using Spark and CloudML to explore parameter space.
\item Designed Bayesian models for Followable-recommendation algorithm. Implemented using Scipy optimization packages.
\item Explored extensions of article-recommendation algorithm using multi-armed and contextual bandit algorithms.
\item Conducted statistical analyses of audience segments and assessed causal impact of new products.
\end{itemize}

{\sl \bf Huffington Post}, NYC, NY {\sl Software Engineering Intern} \hfill {\it Summer 2013}\\
\begin{itemize}
\item Redesigned the core framework of the user-profile API using Scala.
\item HuffPost Hires app (Angular/Clojure/MongoDB). Improved interview process.
\end{itemize}
{\sl \bf SustainabilityExcellence}, Amman, Jordan {\sl Consulting Intern} \hfill {\it Summer 2012}\\
\begin{itemize}
\item Built MYSQL framework for Emir of Qatar's Sustainability Conference.
\end{itemize}

\section{ADDITIONAL \\ EXPERIENCE} 
{\sl \bf New York Times: Diversity Initiatives}: {\sl Co-chair and Founder} of the New York Times Young Professionals Network. {\sl Acknowledged contributor} to Unpublished, a photo-novel on Black history.\\
{\sl \bf Marvel Theater}: {\sl Double Bassist} for critically-acclaimed off-Broadway play. 

\section{ACADEMIC \\HONORS and \\LEADERSHIP}  

{\sl \bf John Jay Scholar}: Neuroscience and Computer Science, Columbia University.\\ 
{\sl \bf Dean's List}: Columbia College\\
{\sl \bf Scholarships}: Intel STS Semi-finalist, National Merit Scholarship\\
{\sl \bf Op-Ed Writer}: Weekly Blogger at Columbia Spectator.\\
\\
{\bf Languages \& Software used in production}: Python, SQL, D3.js, Javascript, JQuery, Java, Scala, C, C++, CUDA, OpenCL, \LaTeX. Google Cloud Services, Amazon Web Services. Spark, DataBricks. Kubernetes, Docker, Drone. SkLearn, Tensorflow, Keras, CVXOpt. NVIDIA.

\end{resume}
\end{document}




